---
title: "Week 2 Homework"
author: "Noah Foilb"
date: "9/4/2020"
output:
  word_document: default
  pdf_document: default
notes: I use R chunks for each answer, even if code is not needed.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 2 Homework

### Working with Excel files

#### 1. Load the libraries to read .csv and .xlsx files (comma-separated variable and Excel files) into R

```{r}
library(readr)  #this library reads .csv files. 
library(readxl) #this library reads Excel files
```







#### 2. Read the Covid-19 Weekly Public Heatlh Report - Raw Data from mass.gov into R.
  * This is an Excel file
  * First, download the file from Blackboard to your computer. 
    *The original file is from mass.gov. If you'd like to view the source, see "Weekly Public Health Report - Raw Data - (Date)" at https://www.mass.gov/info-details/covid-19-response-reporting#covid-19-daily-dashboard-
  * Next, use the appropriate read command to load the Excel file into R. Include the following:
    * This file has multiple worksheets. Read in the sheet entitled "City_Town_Data".
    * There ARE column names in the Excel file
    * We have to code spaces, * and <5 entries from this spreadsheet as Not Available (NA) data. To do so, add na=c("", "*", "<5") after the sheet= specifications (see the section called Data Import Using read_excel() from the week_2B code).
    * Use the assignment operator (<-) to name this dataframe covid_data

```{r}
# This is finding the location of the file and saving that location in Rstudios
file_covid <- "\\Users\\nofoi\\OneDrive\\Desktop\\R studios Data Science\\Homework\\Noah Foilb Week 2\\MA Covid.xlsx"

# This is executing the loctation previously found and saving it as a data set
covid_data <- read_excel(file_covid,col_names=TRUE, sheet="City_Town_Data",na=c("", "*", "<5"))
```







### Data reformatting step
  * Run this piece of code. It will work as long as your dataframe is named covid_data. The case does matter, so if you named your dataframe Covid_data, it won't work
  * You're not expected to know what this code does, but comments are added if you're curious
```{r}
covid_data <- within(covid_data, {
   Total_case_count <- as.numeric(Total_case_count) #codes Total_case_count as numeric data
   Two_Week_Case_Count <- as.numeric(Two_Week_Case_Count) #codes Two_Week_Case_Count as numeric data
   Average_Daily_Incidence_Rate_per_100000 <- as.numeric(Average_Daily_Incidence_Rate_per_100000) #codes Average_Daily_Incidence_Rate_per_100000 as numeric data
   Fraction_positive <- as.numeric(Fraction_positive) #codes Fraction_positive as numeric data
   Relative_Change_in_Case_Count <- factor(Relative_Change_in_Case_Count, levels=c("Lower", "No Change", "Higher")) #codes Relative_Change_in_Case_Count as an ordered factor where in the order Lower<No Change<Higher
   Change_in_fraction_positivity <- factor(Change_in_fraction_positivity, levels=c("Lower", "No Change", "Higher")) #codes Change_in_fraction_positivity as an ordered factor where in the order Lower<No Change<Higher
})
library(dplyr)
covid_data <- filter(covid_data, City_or_Town!="Unknown"&City_or_Town!="State")
```

#### 3. Explore the data using the str() command and answer the following questions:
  * How many numerical (num) variables are in the dataframe?
  * How many character (chr) variables?
  * How many categorical variables (Factor)?
  * How many rows?
  * How many columns?
    * Hint: tibble [503 × 18] would mean there are 503 rows and 18 columns
```{r}
str(covid_data)    # This gives us the structure of the data set

# There are seven "num" variables, one "chr" variable, and two "factor" variables.
# There are 305 rows and 10 columns 
```








#### 4. What are the first three cities/towns in the dataframe? What are the last five? Of these eight cities/towns, how many are missing data for the two week case count?
  * For privacy reason, the state of MA won't report case counts that are <5. Originally, these towns had this entry recorded as <5, but you recoded the entry to NA in your read_excel() command.

```{r}
# The frist three cities are Abington, Acton, and Acushnet.
# The last five are Woburn, Worcester, Worthington, Wrentham, and Yarmouth
# Four are counted as NA
```







### Exploring numerical variables
#### 5. Provide a numerical summary of the number of positive tests in the last 14 days (Positive_Tests_Last_14_days)

```{r}
# By calling the function "summary" and by specifically calling the column heading of Postive_Tests_Last_14_days, we get one column summary
summary(covid_data$Positive_Tests_Last_14_days)
```







#### 6. Provide the quantiles for the number of positive tests in the last 14 days (Positive_Tests_Last_14_days)

```{r}
# By using the function Quantile it given us the quantiles of the data
quantile(covid_data$Positive_Tests_Last_14_days)
```







#### 7. What are the five highest two week case counts (Two_Week_Case_Count)?

```{r}
# By using head to display the first five data, and sort to get the data in order we are able to find the five highesr two week case counts
head(sort(covid_data$Two_Week_Case_Count,decreasing = TRUE,),5)
```







### Exploring categorical variables
 * Before proceeding, recall what are the two categorical (Factor) variables (see question 2). Answer these questions using these categorical variables.
 
#### 8. How many towns had their fraction of positive test results (Change_in_fraction_positivity) higher than last week? Lower? The same?

```{r}
#By using summary we can find the change in a categorical graph
summary(covid_data$Change_in_fraction_positivity)

# 148 lower, 131 the same, and 72 higher.
```







#### 9. How many towns had a decrease in the relative change in case counts (Relative_Change_in_Case_Count)? An increase? No change?

```{r}
#By using summary we can find the change in a categorical graph
summary(covid_data$Relative_Change_in_Case_Count)

# 129 lower, 128 the same, and 94 higher
```






#### 10. Create a two-way table or a contingency table for the two categorical variables from questions 8 and 9 listing how many times each possible combination of the two values occurs. Do you notice any correlation between these two variables?

```{r}
#By using table we can find the change in a categorical graph
table(covid_data$Change_in_fraction_positivity,covid_data$Relative_Change_in_Case_Count)

# there seems to be a strong corelation between the diagnol of this table (LowervsLower, NoChangevsNochange, and HighervsHigher)
```






### Working with .csv files

#### 11. The following website provides data on companies in the S&P 500. The data is in the form of a .csv file. Read the data into R.
  * https://raw.githubusercontent.com/datasets/s-and-p-500-companies-financials/master/data/constituents-financials.csv
  * First, assign the URL to a variable
  * Use the proper read statement to read the file into R
    * The columns DO have column names
    * Make sure you assign the output from the read statement to a variable name

```{r}
#assign the URL as a string to the variable
companies_url <- "https://raw.githubusercontent.com/datasets/s-and-p-500-companies-financials/master/data/constituents-financials.csv"

#inpute the variable into read.csv to aquire the data
companies_data <- read.csv(companies_url)
```






#### 12. What types of variables does the dataset contain (numerical, categorical, etc.), and how many of each type are there?

```{r}
#Gives the structure of the dataset
str(companies_data)

#There are four "chr" and ten "num"
```







#### 13. How many companies are in the dataset (have R report the number of rows)? Does this surprise you?

```{r}
#Use nrow to find the number of rows
nrow(companies_data)

#There are 505 which is a lot more companies then I would have thought
```







#### 14. What are the first three and last three companies in the dataset?

```{r}
#First three
head(companies_data,3)

#Last three
tail(companies_data,3)

#First Three: 3M Company, A.O. Smith Corp and Abbott Laboratories
#Last Three: Zimmer Biomet Holdings, Zions Cancorp, and Zoetis
```







#### 15. Produce a numerical summary of the Market Cap.
  * The column names aren't in a good format for R at the moment. We'll learn more about that later, but for now you'll need to put back quotes around the column names, i.e., `Market Cap`
    * the backquote should be in upper left of your keyboard

```{r}
# Use summary to find the summary
summary(companies_data$`Market.Cap`)
```






#### 16. Produce a table showing the number of companies in each Sector in the S&P500 (the column name is Sector)

```{r}
# use table to make the table
table(companies_data$Sector)
```







